A Solver for Generalised Parikh Images of Regular Languages

### 2021-10-11 abstract/main.tex
improved intro a bit

Parikh images have a wide application within automata, including for the solving
of string constraints in automata-based solvers such as \Ostrich{}
\cite{ostrich}. While it is possible to compute the Parikh image of an automaton
by adapting the method for CFGs of~\cite{generate-parikh-image}, this method
produces clauses with many existentially quantified variables which are costly
to eliminate. This makes many real-world applications intractable. Furthermore,
applications like Unicode require automata with symbolic labels to handle their
large alphabets, increasing the number of variables even more.
Finally, automata-based string solvers compute Parikh images on products of
automata, derived from conjunctions of string constraints. Using
\cite{generate-parikh-image} this would require the up-front computation of the
product before its Parikh image, running the risk of an exponential blow-up.

>>>>

Parikh images are a central notion in automata theory and context-free grammars,
with wide-ranging applications, including the solving
of string constraints in automata-based solvers such as \Ostrich{}
\cite{ostrich}. In this work, we focus on the efficient computation
of Parikh images, or points within the Parikh image, of finite-state
automata. While it is possible to compute the Parikh image of an automaton
by adapting the method for context-free grammars
 of~\cite{generate-parikh-image}, this method
produces clauses with many existentially quantified variables which are costly
to eliminate. This makes many real-world applications intractable. Furthermore,
applications like Unicode require automata with symbolic labels to handle their
large alphabets, increasing the number of variables even more.
Finally, automata-based string solvers compute Parikh images on products of
automata, derived from conjunctions of string constraints. Using
\cite{generate-parikh-image} this would require the up-front computation of the
product before its Parikh image, running the risk of an exponential blow-up.
